Eco Tracker Appendix

### 2025-02-20 paper/appendix.tex
Update to the agent to make it faster
- added comparissons to other types of baselines

>>>>

\section{Solar Baseline}
\begin{table}[h!]
  \centering
  \begin{tabular}{lcccccc}
  \hline
   & Baseline 0 & Baseline 1 & Baseline 2 & Baseline 3 & Baseline 4 & Agent \\
  \hline
  Transmission Actions & 960 & 480 & 320 & 240 & 190 & 308 \\
  Collection Actions   & 0   & 480 & 640 & 720 & 770 & 652 \\
  Sleep Actions        & 0   & 0   & 0   & 0   & 0   & 0   \\
  Avg. Message Count   & 709 & 766.5 & 769 & 782 & 805 & 790 \\
  Avg. Power Level     & 45  & 52  & 55  & 55  & 57  & 55  \\
  \hline
  \end{tabular}
  \caption{Comparison of Baselines and Agent Performance}
  \label{table:baselines_vs_agent}
  \end{table}
